Interactive results review

### 2024-07-25 nbs/guides/interactive/interactive.qmd
fix(nbs): move interactive guide to subfolder
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Interactive results review
---

@@

```{python}
from flytekit.remote.remote import FlyteRemote
from flytekit.configuration import Config

@@

```{python}
workflow_outputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-argo-nix-bui-5c9ebf8-dev-1hk-d5805de62e8044f79d4/f26c1pjy-0-dn0-0-dn7/o"
)
```

@@

```{python}
from omegaconf import OmegaConf
from flytekit.interaction.string_literals import literal_map_string_repr

@@

```{python}
from pyrovelocity.io.gcs import download_blob_from_uri

download_blob_from_uri(outputs_dictconfig.o0.dataframe.path)
```

>>>>

---
title: Interactive results review
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
toc: true
number-sections: true
highlight-style: pygments
csl: bibstyle.csl
lightbox: auto
format:
  html:
    html-math-method: katex
  ipynb: default
---

```{python}
#| label: enable-autoreload
#| code-fold: true
#| output: false
%load_ext autoreload
%autoreload 2 
```

@@

```{python}
#| label: instantiate-remote-client
from flytekit.remote.remote import FlyteRemote
from flytekit.configuration import Config

@@

```{python}
#| label: get-remote-outputs
workflow_outputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-argo-nix-bui-5c9ebf8-dev-1hk-d5805de62e8044f79d4/f26c1pjy-0-dn0-0-dn6/o"
)
```

@@

```{python}
#| label: create-outputs-dict
from omegaconf import OmegaConf
from flytekit.interaction.string_literals import literal_map_string_repr

@@

```{python}
#| label: download-outputs
from pyrovelocity.io.gcs import download_blob_from_uri

pyrovelocity_data = download_blob_from_uri(
    outputs_dictconfig.o0.pyrovelocity_data.path
)
postprocessed_data = download_blob_from_uri(
    outputs_dictconfig.o0.postprocessed_data.path
)
```
